How I use R Markdown to write research papers

### 2020-11-18 text/20/markdown-papers.Rmd
Added interval-censored.md

**Figures** R can produce beautiful graphs, and with R Markdown, you can insert these graphs anywhere in your document. You can't control page breaks easily in R Markdown, however. Here's an example of a simple graph.

@@

@@

>>>>

**Figures**

R can produce beautiful graphs, and with R Markdown, you can insert these graphs anywhere in your document. You can't control page breaks easily in R Markdown, however. Here's an example of a simple graph.

@@

**Output formats**

You can specify a variety of output formats. The ones I use most often are

+ docx
+ html
+ pdf
+ pptx

The pdf option requires that you have a version of LaTeX installed on your computer. I use [MikTeX](https://miktex.org/), but others work just fine.

@@

The bibliography always appears at the end of the document.

**Final comments**

Most of the people that I collaborate with do not use R Markdown, so I typically will start a draft in R Markdown, but when it gets to the point where I can share it with my collaborators, I send the document in Word format and we make any further changes there. If I am the sole author, then I can keep the file in R Markdown.
